A Comparison of Graph Processing Systems

### 2020-09-29 documentation/paper/main.tex
ein weiteres Zitat

% \bibliographystyle{IEEEtran}
% \bibliography{literature}

% Alles ab hier kommt aus main.bbl

@@

@@

\bibitem{pbbs}
\BIBentryALTinterwordspacing
J.~Shun, G.~Blelloch, J.~Fineman, P.~Gibbons, A.~Kyrola, K.~Tangwonsan, and
  H.~V. Simhadri. (2020, Aug.) {Problem Based Benchmark Suite }. [Online].
  Available: \url{http://www.cs.cmu.edu/~pbbs/}
\BIBentrySTDinterwordspacing

\end{thebibliography}

>>>>

%\bibliographystyle{IEEEtran}
%\bibliography{literature}

@@

\bibitem{viralMarketing}
\BIBentryALTinterwordspacing
P.~Domingos and M.~Richardson, ``Mining the network value of customers,'' in
  \emph{Proceedings of the Seventh ACM SIGKDD International Conference on
  Knowledge Discovery and Data Mining}, ser. KDD '01.\hskip 1em plus 0.5em
  minus 0.4em\relax New York, NY, USA: Association for Computing Machinery,
  2001, p. 57–66. [Online]. Available:
  \url{https://doi.org/10.1145/502512.502525}
\BIBentrySTDinterwordspacing

@@

\bibitem{pbbs}
\BIBentryALTinterwordspacing
J.~Shun, G.~Blelloch, J.~Fineman, P.~Gibbons, A.~Kyrola, K.~Tangwonsan, and
  H.~V. Simhadri. (2020, Aug.) {Problem Based Benchmark Suite }. [Online].
  Available: \url{http://www.cs.cmu.edu/~pbbs/}
\BIBentrySTDinterwordspacing
\end{thebibliography}
